---
title: "Class Compromise"
author: Alper Duman
date: 04/24/2021
output: pdf_document
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Introduction

Joan Robinson famously claimed that worse than being exploited is not-to-be exploited.
A worker is exploited while she works.
An unemployed worker is not exploited.
The downside is she has no income.
Generalizing this observation to the whole economy we can grasp the structural dependence of
workers on capitalists.
Unless the capitalists invest and demand workers for exploitation and generation of surplus value, workers have no wage income. 
Since the capitalists are the ultimate controllers of means of production, their behavior is pivotal for the dynamics of the capitalist economy. 

# Class Conflict and Compromise

At any given time the total output/income is the sum of wages and profits. 

$Y_{t} = W_{t} + P_{t}$

Assume that the worker will only give their consent and work efficiently if their wages go up following a 
predetermined path such as

$W_{t}^{d}=W_{t-1} + \alpha P_{t-1}$

where $\alpha$ is the rate of past period profits to be transferred to workers. 
Obviously $\alpha=1$ reflects a workers' revolution; meaning all the profits are confiscated.
Therefore $0<\alpha < 1$ is a small but a positive number.

The output on the hand depends on the behaviour of the capitalists.

$Y_{t+1} = W_{t} + (1 + s/k)P_{t}$

where $s$ is the saving rate out of profits and $k$ is the capital-output ratio.
At the steady state

$W_{t}^{d}=W_{t}$




## Militancy


## Saving Rate of the Capitalists

# Dynamic Model

The advanced capitalist economies require $s=0.5$ and $\alpha=0.075$ with an equal split of income initially.
For Turkey, $s=0.4$ and $\alpha=0.04$ with a 70% profit share initially
reproduces current outcome of 60% / 40% split for capital 
and labor respectively.

```{r Y}
Y <- as.numeric()
s <- 0.3
alpha <- 0.03
#s <- seq(0.01:0.9, by=0.01)
# r <- seq(0.01:0.9, by=0.01)
k <- 4
P0 <- 70
W0 <- 30
W <- as.numeric()
P <- as.numeric()
```

```{r loop}
Y[1] <- W0 + (1 + s/k)*P0
W[1] <- W0 + alpha*P0
P[1] <- Y[1]-W[1]
for (i in 2:200) {
Y[i] <- W[i-1] + (1+s/k)*P[i-1]
W[i] <- W[i-1] + alpha*P[i-1]
P[i] <- Y[i]-W[i]
}
```

```{r plot}
plot(log(Y), W/P)
```

# Conclusion


